ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-07-24 pyked.tex
minor wording fix

\pk{}~\autocite{PyKED} relies on well-established scientific Python software tools.
These include NumPy~\autocite{vanderWalt:2011np} and Pandas~\autocite{pandas,McKinney2010}
for array manipulation, Pint~\autocite{Grecco2016} for interpreting and converting
between units, PyYAML~\autocite{pyyaml} for parsing YAML
files, and Cerberus for validating \ck{} files~\autocite{cerberus}.
Furthermore, \pk{} includes extensive unit, integration, and functional tests
that ensure all aspects of the software operate as intended; others have pointed
out the importance of automated testing in scientific software~\autocite{Wilson:bestpractices}.
\pk{} relies on pytest~\autocite{pytest:3.0.1} for unit testing, and currently has
100\% line and branch coverage for all of the executable code in the repository. This
means that the tests execute every line of code at least once, and every branch statement
(e.g., if-then-else statement) is tested so that every condition is executed at least
once.

Travis-CI\footnote{\url{https://travis-ci.org/pr-omethe-us/PyKED}} provides continuous
integration service, including running the test suite, building and distributing binary
installer packages, and building and publishing the online documentation. This automation
ensures that the test suite is run after every change to the source code, the
documentation is up-to-date with the latest changes, and releasing new versions is as
streamlined as possible.

>>>>

\pk{}~\autocite{PyKED} relies on well-established scientific Python software tools.
These include NumPy~\autocite{vanderWalt:2011np} and Pandas~\autocite{pandas,McKinney2010}
for array manipulation, Pint~\autocite{Grecco2016} for interpreting and converting
between units, PyYAML~\autocite{pyyaml} for parsing YAML
files, and Cerberus for validating \ck{} files~\autocite{cerberus}.
Furthermore, \pk{} includes extensive unit, integration, and functional tests
that ensure all aspects of the software operate as intended; others have pointed
out the importance of automated testing in scientific software~\autocite{Wilson:bestpractices}.
\pk{} relies on pytest~\autocite{pytest:3.0.1} for automated testing, and currently has
100\% line and branch coverage for all of the executable code in the repository. This
means that the tests execute every line of code at least once, and evaluate
every branch statement (e.g., if-then-else statements) to execute every condition
at least once.

Travis-CI\footnote{\url{https://travis-ci.org/pr-omethe-us/PyKED}} provides continuous
integration service, including running the test suite, building and distributing binary
installer packages, and building and publishing the online documentation. This automation
runs the test suite after every change to the source code, keeps the documentation
up-to-date with the latest changes, and streamlines the release of new versions.
